### 2017-11-07 exchange-draft/adjoint-model.tex
Adding a new directory.

Our adjoint model, SMCC-Lambek model, has a similar structure as Benton's LNL model \cite{}.
Benton's LNL model consists of a symmetric monoidal adjunction $F:\cat{C}\dashv\cat{L}:G$
between a cartesian closed category $\cat{C}$ and a symmetric monoidal closed category
$\cat{L}$.

\begin{definition}
  A \textbf{SMCC-Lambek model} consists of
  \begin{itemize}
  \item a symmetric monoidal closed category $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$;
  \item a Lambek category $(\cat{L},\tri,I',\alpha',\lambda',\rho')$;
  \item a monoidal adjunction $F:\cat{C}\dashv\cat{L}:G$, where $F:\cat{C}\rightarrow\cat{L}$
        and $G:\cat{L}\rightarrow\cat{C}$ are monoidal functors.
  \end{itemize}
\end{definition}

Thus, in a SMCC-Lambek model, the following four diagrams commute because $\eta$ and
$\varepsilon$ are monoidal natural transformations:
\begin{mathpar}
\bfig
  \square/=`->`->`/<1600,400>[
    X\otimes Y`X\otimes Y`GFX\otimes GFY`GF(X\otimes Y);
    id_{X\otimes Y}`\eta_X\otimes\eta_Y`\eta_{X\otimes Y}`]
  \morphism<800,0>[GFX\otimes GFY`G(FX\otimes FY);\n{FX,FY}]
  \morphism(800,0)<800,0>[G(FX\otimes FY)`GF(X\otimes Y);G\m{X,Y}]
\efig
\and
\bfig
  \square/->`=`<-`->/<400,400>[I`GFI`I`GI';\eta_I``G\m{I}`\n{I'}]
\efig
\end{mathpar}
\begin{mathpar}
\bfig
  \square/`->`->`=/<1600,400>[
    FGA\otimes FGB`FG(A\otimes B)`A\otimes B`A\otimes B;
    `
    \varepsilon_A\otimes\varepsilon_B`\varepsilon_{A\otimes B}`]
  \morphism(0,400)<800,0>[FGA\otimes FGB`F(GA\otimes GB);\m{GA,GB}]
  \morphism(800,400)<800,0>[F(GA\otimes GB)`FG(A\otimes B);F\n{A,B}]
\efig
\and
\bfig
  \square/->`<-`=`<-/<400,400>[FGI'`I'`FI`I';\varepsilon_{I'}`F\n{I'}``\m{I}]
\efig
\end{mathpar}
And the following two diagrams commute because of the adjunction:
\begin{mathpar}
\bfig
  \Vtriangle/->`=`->/<400,400>[FX`FGFX`FX;F\eta_X``\varepsilon_{FX}]
\efig
\and
\bfig
  \Vtriangle/->`=`->/<400,400>[GA`GFGA`GA;\eta_{GA}``G\varepsilon_A]
\efig
\end{mathpar}
Following the tradition, we use letters $X$, $Y$, $Z$ for objects in $\cat{C}$ and $A$, $B$, $C$
for objects in $\cat{L}$. The following lemmas and theorems establish the essential properties
of the monad and the comomad derived from the adjunction.

@@

  The monad on the symmetric monoidal closed category $\cat{C}$ in a SMCC-Lambek model is
  monoidal.

@@

  We define the monad $T$ on the $\cat{C}$ in the adjunction of a SMCC-Lambek model as $T=GF$,
  and the two corresponding natural transformations $\eta:id_\cat{C}\rightarrow T$ and
  $\mu:T^2\rightarrow T$ as
  $$\eta_X:X\rightarrow GFX \qquad\qquad\qquad \mu_X=G\varepsilon_{FX}:GFGFX\rightarrow GFX$$
  where $\eta$ is the unit and $\varepsilon:FG\rightarrow id_\cat{L}$ is the counit of the
  adjunction $F:\cat{C}\dashv\cat{L}:G$. Since the adjunction is monoidal, then $(F,\m{})$ and
  $(G,\n{})$ are monoidal functors. Thus, we have

@@

  The monad $T$ being monoidal means

@@

However, the monad is not symmetric becauase the following diagram does not commute, for the
lambek category $\cat{L}$ is not symmetric.
\begin{mathpar}
\bfig
  \ptriangle/->`->`/<900,400>[
    GFX\otimes GFY`GFY\otimes GFX`G(FX\tri FY);\e{GFX,GFY}`\n{FX,FY}`]
  \morphism(900,400)<900,0>[GFY\otimes GFX`G(FY\tri FX);\n{FY,FX}]
  \dtriangle(900,0)/`->`->/<900,400>[
    G(FY\tri FX)`GF(X\otimes Y)`GF(Y\otimes X);`G\m{Y,X}`GF\e{X,Y}]
  \morphism|b|<900,0>[G(FX\tri FY)`GF(X\otimes Y);G\m{X,Y}]
\efig
\end{mathpar}

@@

  The monad on the symmetric monoidal closed category in a SMCC-Lambek model is strong.

@@

  Let $F:\cat{C}\vdash\cat{L}:G$ be a SMCC-Lambek model, where
  $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$ is symmetric monoidal closed,
  $(\cat{L},\tri,I',\alpha',\lambda',\rho')$ is a Lambek category, and $(F,\m{})$ and
  $(G,\n{})$ are monoidal functors. We have proved that the monad $(T=GF,\eta,\mu)$ is monoidal
  with the natural transformation $\t{X,Y}:TX\otimes TY\rightarrow T(X\otimes Y)$ and the
  morphism $\t{I}:I\rightarrow TI$ defined as in Lemma~\ref{lem:monoidal-monad}. \\

@@

  $\eta$ are $\alpha$ natural transformations and $T$ is monoidal:

@@

\begin{lemma}[\cite{kock1970monads}]
  Let $\cat{M}$ be a symmetric monoidal category and $T$ be a strong monad on $\cat{M}$. Then
  $T$ is symmetric iff it is commutative.
\end{lemma}

\begin{theorem}
  The monad on the SMCC in a SMCC-Lambek model is monoidal and non-commutative.
\end{theorem}

\begin{lemma}
  The comonad on the Lambek category in a SMCC-Lambek model is monoidal.
\end{lemma}
\begin{proof}
  We define the comonad $S$ on the Lambek category $\cat{L}$ in the adjunction
  $F:\cat{C}\vdash\cat{L}:G$ of a SMCC-Lambek model as $S=FG$. The two corresponding natural
  transformations $\varepsilon:S\rightarrow id_\cat{L}$ and $\delta:S\rightarrow S^2$ are
  defined as
  $$\varepsilon_A:SA\rightarrow A \qquad\qquad\qquad \delta_A=F\eta_{GA}:SA\rightarrow S^2A$$
  where $\varepsilon$ is the counit and $\eta:id_\cat{L}\rightarrow GF$ is the unit of the
  adjunction, and $(F,\m{})$ and $(G,\n{})$ are monoidal functors. Thus, we have
  $$\s{A,B}=F\n{A,B}\circ\m{GA,GB}:SA\tri SB\rightarrow SA\tri SB \qquad\qquad\qquad
  \s{I}=F\n{I'}\circ\m{I}:I'\rightarrow SI'$$
  The comonad $S$ being monoidal means
  \begin{enumerate}
  \item $S$ is a monoidal functor, i.e. the following diagrams commute:
        \begin{mathpar}
        \bfig
          \hSquares/->`->`->``->`->`->/<400>[
            (SA\tri SB)\tri SC`SA\tri(SB\tri SC)`SA\tri S(B\tri C)`
            S(A\tri B)\tri SC`S((A\tri B)\tri C)`S(A\tri(B\tri C));
            \alpha_{SA,SB,SC}'`id_{SA}\tri\s{B,C}`\s{A,B}\tri id_{SC}``
            \s{A,B\tri C}`\s{A\tri B,C}`S\alpha_{A,B,C}']
        \efig
        \and
        \bfig
          \square/->`->`<-`->/<600,400>[
            I'\tri SA`SA`SI'\tri SA`S(I'\tri A);
            \lambda_{SA}'`\s{I'}\tri id_{SA}`S\lambda_A'`\s{I',A}]
        \efig
        \and
        \bfig
          \square/->`->`<-`->/<600,400>[
            SA\tri I'`SA`SA\tri SI'`S(A\tri I');
            \rho_{SA}'`id_{SA}'\tri\s{I'}`S\rho_A'`\s{A,I'}]
        \efig
        \end{mathpar}
  \item $\varepsilon$ is a monoidal natural transformation:
        \begin{mathpar}
        \bfig
          \square/->`->`->`=/<600,400>[
            SA\tri SB`S(A\tri B)`A\tri B`A\tri B;
            \s{A,B}`\varepsilon_A\tri\varepsilon_B`\varepsilon_{A\tri B}`]
        \efig
        \and
        \bfig
          \Vtriangle/->`<-`=/<400,400>[SI'`I'`I';\varepsilon_{I'}`\s{I'}`]
        \efig
        \end{mathpar}
  \item $\delta$ is a monoidal natural transformation:
        \begin{mathpar}
        \bfig
          \square/->`->`->`/<1500,400>[
            SA\tri SA`S(A\tri B)`S^2A\tri S^2B`S^2(A\tri B);
            \s{A,B}`\delta_A\tri\delta_B`\delta_{A\tri B}`]
          \morphism<800,0>[S^2A\tri S^2B`S(SA\tri SB);\s{SA,SB}]
          \morphism(800,0)<700,0>[S(SA\tri SB)`S^2(A\tri B);S\s{A,B}]
        \efig
        \and
        \bfig
          \square/->`<-`<-`->/<400,400>[
            SI'`S^2I'`I'`SI';\delta_{I'}`\s{I'}`S\s{I'}`\s{I'}]
        \efig
        \end{mathpar}
  \end{enumerate}
  The proof for the commutativity of the diagrams are similar as the proof in
  Lemma~\ref{lem:monoidal-monad}. We do not include the proof here for simplicity.
\end{proof}

The comonad $S$ on the Lambek category $\cat{L}$ of the adjunction is clearly not symmetric
because $\cat{L}$ is not. However, it is symmetric on the co-Eilenberg-Moore category of the
comonad.

@@

\begin{lemma}
  \label{lem:em-exchange}
  Given a SMCC-Lambek model $F:\cat{C}\dashv\cat{L}:G$ and the comonad $S$ on $\cat{L}$, the
  co-Eilenberg-Moore category $\cat{L}^S$ of has an exchange natural transformation
  $\e{A,B}^S:A\tri B\rightarrow B\tri A$.
\end{lemma}
\begin{proof}
  We define the exchange $\e{A,B}^S:A\tri B\rightarrow B\tri A$ as
  $$\bfig
    \morphism<600,0>[A\tri B`FGA\tri FGB;h_A\tri h_B]
    \morphism(600,0)<800,0>[FGA\tri FGB`F(GA\otimes GB);\m{GA,GB}]
    \morphism(1400,0)<800,0>[F(GA\otimes GB)`F(GB\otimes GA);F\e{GA,GB}]
    \morphism(2200,0)<700,0>[F(GB\otimes GA)`FG(B\tri A);F\n{B,A}]
    \morphism(2900,0)<500,0>[FG(B\tri A)`B\tri A;\varepsilon_{B\tri A}]
  \efig$$
  in which $(F,\m{})$ and $(G,\n{})$ are monoidal functors, and $\e{}$ is the exchange for
  $\cat{C}$. $\e{}^S$ is a natural transformation because the following diagrams commute for
  morphisms $f:A\rightarrow A'$ and $g:B\rightarrow B'$:
  \begin{mathpar}
  \bfig
    \square|almb|<700,400>[
      A\tri B`FGA\tri FGB`A'\tri B'`FGA'\tri FGB';
      h_A\tri h_B`f\tri g`FGf\tri FGg`h_{A'}\tri h_{B'}]
    \square(700,0)|ammb|/->``->`->/<800,400>[
      FGA\tri FGB`F(GA\otimes GB)`FGA'\tri FGB'`F(GA'\otimes GB');
      \m{GA,GB}``F(Gf\otimes Gg)`\m{GA',GB'}]
    \square(1500,0)|ammb|/->``->`->/<800,400>[
      F(GA\otimes GB)`F(GB\otimes GA)`F(GA'\otimes GB')`F(GB'\otimes GA');
      F\e{A,B}``F(Gg\otimes Gf)`F\e{A',B'}]
    \square(2300,0)|ammb|/->``->`->/<800,400>[
      F(GB\otimes GA)`FG(B\tri A)`F(GB'\otimes GA')`FG(B'\tri A');
      F\n{B,A}``FG(g\tri f)`F\n{B',A'}]
    \square(3100,0)|amrb|/->``->`->/<600,400>[
      FG(B\tri A)`B\tri A`FG(B'\tri A')`B'\tri A';
      \varepsilon_{B\tri A}``g\tri f`\varepsilon_{B'\tri A'}]
  \efig
  \end{mathpar}
\end{proof}

@@

    \Vtrianglepair|aammm|/->`->`<-``<-/<1000,400>[

@@

    \qtriangle(2000,0)|amr|/=`<-`->/<1000,400>[

@@

    \dtriangle(1000,0)|mmm|/`<-`->/<1000,400>[

@@

    \btriangle(0,-400)|lmm|/->`<-`/<1000,400>[

@@

    \btriangle(1000,-400)|mmm|/<-``->/<2000,400>[

@@

    \qtriangle(2000,-400)|mmr|/`<-`->/<1000,400>[

@@

    \btriangle(0,-800)|lmm|/->`<-`/<2000,400>[

@@

    \morphism(1000,-400)|m|<1000,-400>[

@@

    \dtriangle(2000,-800)|mra|/`->`->/<1000,400>[

@@

    \square(0,-1200)|almb|/<-`->`->`->/<1000,400>[

@@

    \morphism(1000,-800)|b|/<-/<1000,0>[

@@

    \dtriangle(1000,-1200)/`->`<-/<2000,400>[

@@

    \morphism(1000,-800)|m|<2000,-400>[

@@

    \morphism(500,50)//<0,0>[`;(1)]
    \morphism(500,-300)//<0,0>[`;(2)]

@@

    \morphism(500,-950)//<0,0>[`;(4)]
    \morphism(1000,300)//<0,0>[`;(5)]
    \morphism(1600,200)//<0,0>[`;(6)]

@@

    \morphism(1300,-950)//<0,0>[`;(9)]
    \morphism(2700,-900)//<0,0>[`;(10)]
    \morphism(2800,300)//<0,0>[`;(11)]
    \morphism(2500,50)//<0,0>[`;(12)]

@@

  The third diagram commutes as follows, which uses Lemma~\ref{lem:emex}.

@@

    \morphism(2200,-2000)|m|<0,-400>[

@@

    \morphism(1500,-2200)|m|<0,-400>[F(GB\otimes G(A\tri C))`FG(B\tri(A\tri C));F\n{B,A\tri C}]

@@

    \morphism(1500,-2600)|m|<-1500,0>[

@@

    \morphism(3200,-3000)|m|<-1000,600>[FG((B\tri C)\tri A)`FG(B\tri(C\tri A));FG\alpha_{B,C,A}]

@@

>>>>

Our adjoint model, Lambek Adjoint Model (LAM), has a similar structure as Benton's LNL model
\cite{}. Benton's LNL model consists of a symmetric monoidal adjunction
$F:\cat{C}\dashv\cat{L}:G$ between a cartesian closed category $\cat{C}$ and a symmetric
monoidal closed category $\cat{L}$. LAM consists of a monoidal adjunction between a symmetric
monoidal closed category and a Lambek category.

\begin{definition}
  A \textbf{Lambek Adjoint Model (LAM)} $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$ consists of
  \begin{itemize}
  \item a symmetric monoidal closed category $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$;
  \item a Lambek category $(\cat{L},\tri,I',\alpha',\lambda',\rho')$;
  \item a monoidal adjunction $F:\cat{C}\dashv\cat{L}:G$ with unit $\eta_X:X\rightarrow GFX$ and
        counit $\varepsilon:FG\rightarrow id_\cat{L}$, where $(F:\cat{C}\rightarrow\cat{L}, m)$
        and $(G:\cat{L}\rightarrow\cat{C}, n)$ are monoidal functors.
  \end{itemize}
\end{definition}

Thus, in LAM, the following four diagrams commute because $\eta$ and $\varepsilon$ are monoidal
natural transformations:
\begin{mathpar}
\bfig
  \square/=`->`->`/<1600,400>[
    X\otimes Y`X\otimes Y`GFX\otimes GFY`GF(X\otimes Y);
    id_{X\otimes Y}`\eta_X\otimes\eta_Y`\eta_{X\otimes Y}`]
  \morphism<800,0>[GFX\otimes GFY`G(FX\otimes FY);\n{FX,FY}]
  \morphism(800,0)<800,0>[G(FX\otimes FY)`GF(X\otimes Y);G\m{X,Y}]
\efig
\and
\bfig
  \square/->`=`<-`->/<400,400>[I`GFI`I`GI';\eta_I``G\m{I}`\n{I'}]
\efig
\end{mathpar}
\begin{mathpar}
\bfig
  \square/`->`->`=/<1600,400>[
    FGA\otimes FGB`FG(A\otimes B)`A\otimes B`A\otimes B;
    `
    \varepsilon_A\otimes\varepsilon_B`\varepsilon_{A\otimes B}`]
  \morphism(0,400)<800,0>[FGA\otimes FGB`F(GA\otimes GB);\m{GA,GB}]
  \morphism(800,400)<800,0>[F(GA\otimes GB)`FG(A\otimes B);F\n{A,B}]
\efig
\and
\bfig
  \square/->`<-`=`<-/<400,400>[FGI'`I'`FI`I';\varepsilon_{I'}`F\n{I'}``\m{I}]
\efig
\end{mathpar}
And the following two triangles commute because of the adjunction:
\begin{mathpar}
\bfig
  \Vtriangle/->`=`->/<400,400>[FX`FGFX`FX;F\eta_X``\varepsilon_{FX}]
\efig
\and
\bfig
  \Vtriangle/->`=`->/<400,400>[GA`GFGA`GA;\eta_{GA}``G\varepsilon_A]
\efig
\end{mathpar}

Following the tradition, we use letters $X$, $Y$, $Z$ for objects in $\cat{C}$ and $A$, $B$, $C$
for objects in $\cat{L}$. The rest of this section proves essential properties of a LAM.

\subsection{An Isomorphism}

Let $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$ be a LAM, where $(F,\m{})$ and $(G,\n{})$ are
monoidal functors. Similarly as in Benton's LNL model, $\m{X,Y}$ are components of a natural
isomorphism and $\m{I}$ is an isomorphism. This is essential for deriving certain rules of
our non-commutative linear logic, such as tensor elimination in natural deduction.

We define the inverses of $\m{X,Y}:FX\tri FY\rightarrow F(X\otimes Y)$ and
$\m{I}:I'\rightarrow FI$ as:

\begin{mathpar}
\bfig
  \morphism<1000,0>[\p{X,Y}:F(X\otimes Y)`F(GFX\otimes GFY);F(\eta_X\otimes\eta_Y)]
  \morphism(1000,0)<900,0>[F(GFX\otimes GFY)`FG(FX\tri FY);F\n{FX,FY}]
  \morphism(1900,0)<750,0>[FG(FX\tri FY)`FX\tri FY;\varepsilon_{FX\tri FX}]
\efig
\and
\bfig
  \morphism<500,0>[\p{I}:FI`FGI';F\n{I'}]
  \morphism(500,0)<400,0>[FGI'`I';\varepsilon_{I'}]
\efig
\end{mathpar}

\begin{theorem}
  $\m{X,Y}$ are components of a natural isomorphism and their inverses are $\p{X,Y}$.
\end{theorem}
\begin{proof}
  We need to show that $\m{X,Y}\circ\p{X,Y}=id_{F(X\otimes Y)}$ and
  $\p{X,Y}\circ\m{X,Y}=id_{FX\tri FX}$. The two equations hold because the following diagrams
  commute: (1)-adjunction; (2)-$\eta$ is a monoidal natural transformation; (3)-naturality of
  $\varepsilon$; (4)-adjunction; (5)-naturality of $\m{}$; (6)-$\varepsilon$ is a monoidal
  natural transformation.
  \begin{mathpar}
  \bfig
    \square/->`=`->`/<1600,800>[
      F(X\otimes Y)`F(GFX\otimes GFY)`F(X\otimes Y)`FG(FX\tri FY);
      F(\eta_X\otimes\eta_Y)``F\n{FX,FY}`]
    \Atrianglepair|mmmbb|/->``->`<-`<-/<800,400>[
      FGF(X\otimes Y)`F(X\otimes Y)`FX\tri FY`FG(FX\tri FY);
      \varepsilon_{F(X\otimes Y)}``FG\m{X,Y}`\m{X,Y}`\varepsilon_{FX\tri FY}]
    \morphism(0,800)|m|<800,-400>[F(X\otimes Y)`FGF(X\otimes Y);F\eta_{X\otimes Y}]
    \morphism(300,450)//<0,0>[`;(1)]
    \morphism(1200,600)//<0,0>[`;(2)]
    \morphism(800,200)//<0,0>[`;(3)]
  \efig
  \and
  \bfig
    \square/->`=`->`/<1800,800>[
      FX\tri FY`F(X\otimes Y)`FX\tri FY`F(GFX\otimes GFY);
      \m{X,Y}``F(\eta_X\otimes\eta_Y)`]
    \Atrianglepair|mmmbb|/->``->`<-`<-/<900,400>[
      FGFX\tri FGFY`FX\tri FY`FG(FX\tri FY)`F(GFX\otimes GFY);
      \varepsilon_{FX}\tri\varepsilon_{FY}``\m{GFX,GFY}`\varepsilon_{FX\tri FY}`F\n{FX,FY}]
    \morphism(0,800)|m|<900,-400>[FX\tri FY`FGFX\tri FGFY;F\eta_X\tri F\eta_Y]
    \morphism(300,450)//<0,0>[`;(4)]
    \morphism(1300,600)//<0,0>[`;(5)]
    \morphism(900,200)//<0,0>[`;(6)]
  \efig
  \end{mathpar}
\end{proof}

\begin{theorem}
  $\m{I}$ is an isomorphism and its inverse is $\p{I}$.
\end{theorem}
\begin{proof}
  This is equivalent to equations $\m{I}\circ\p{I}=id_{FI}$ and $\p{I}\circ\m{I}=id_{I'}$,
  equivalent to the following diagrams, which commute because $\varepsilon$ is a monoidal
  natural transformation.
  \begin{mathpar}
  \bfig
    \square/->`=`->`<-/<400,400>[FI`FGI'`FI`I';F\n{I'}``\varepsilon_{I'}`\m{I}]
  \efig
  \and
  \bfig
    \square/->`=`->`<-/<400,400>[I'`FI`I'`FGI';\m{I}``F\n{I'}`\varepsilon_{I'}]
  \efig
  \end{mathpar}
\end{proof}

\subsection{Monad on $\cat{C}$}

We first show that the monad on $\cat{C}$ in LAM is strong but non-commutative. In Benton's
LNL model, the monad on the cartesian closed category is commutative.

@@

  The monad on the symmetric monoidal closed category $\cat{C}$ in LAM is monoidal.

@@

  Let $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$ be a LAM. We define the monad
  $(T,\eta:id_\cat{C}\rightarrow T,\mu:T^2\rightarrow T)$ on $\cat{C}$ as
  $$T=GF \qquad\qquad\qquad \eta_X:X\rightarrow GFX \qquad\qquad\qquad \mu_X=G\varepsilon_{FX}:GFGFX\rightarrow GFX$$
  Since $(F,\m{})$ and $(G,\n{})$ are monoidal functors, we have

@@

  The monad $T$ being monoidal means:

@@

However, the monad is not symmetric becauase the following diagram does not commute, for the
Lambek category $\cat{L}$ is not symmetric.
\begin{mathpar}
\bfig
  \ptriangle/->`->`/<900,400>[
    GFX\otimes GFY`GFY\otimes GFX`G(FX\tri FY);\e{GFX,GFY}`\n{FX,FY}`]
  \morphism(900,400)<900,0>[GFY\otimes GFX`G(FY\tri FX);\n{FY,FX}]
  \dtriangle(900,0)/`->`->/<900,400>[
    G(FY\tri FX)`GF(X\otimes Y)`GF(Y\otimes X);`G\m{Y,X}`GF\e{X,Y}]
  \morphism|b|<900,0>[G(FX\tri FY)`GF(X\otimes Y);G\m{X,Y}]
\efig
\end{mathpar}

@@

  The monad on the symmetric monoidal closed category in LAM is strong.

@@

  Let $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$ be a LAM, where
  $(\cat{C},\otimes,I,\alpha,\lambda,\rho)$ is symmetric monoidal closed, \\
  $(\cat{L},\tri,I',\alpha',\lambda',\rho')$ is Lambek. In Lemma~\ref{lem:monoidal-monad}, we
  have proved that the monad $(T=GF,\eta,\mu)$ is monoidal with the natural transformation
  $\t{X,Y}:TX\otimes TY\rightarrow T(X\otimes Y)$ and the morphism $\t{I}:I\rightarrow TI$. \\

@@

  $\eta$ and $\alpha$ are natural transformations and $T$ is monoidal:

@@

The following lemma is adopted from \cite{}.
\begin{lemma}
\label{lem:monad-com-iff-sym}
  Let $\cat{M}$ be a symmetric monoidal category and $T$ be a strong monad on $\cat{M}$. Then
  $T$ is commutative iff it is symmetric.
\end{lemma}

\begin{theorem}
  The monad on the SMCC in LAM is strong but non-commutative.
\end{theorem}
\begin{proof}
  The proof is obvious. Based on Lemma~\ref{lem:strong-monad} and
  Lemma~\ref{lem:monad-com-iff-sym}, the monad is non-commutative. 
\end{proof}

\subsection{Comonad on $\cat{L}$}

\begin{lemma}
  The comonad on the Lambek category in a LAM is monoidal.
\end{lemma}
\begin{proof}
  We define the comonad $(S,\varepsilon:S\rightarrow id_\cat{L},\delta:S\rightarrow S^2)$ on
  the Lambek category $\cat{L}$ as:
  $$S=FG \qquad\qquad\qquad \varepsilon_A:SA\rightarrow A \qquad\qquad\qquad \delta_A=F\eta_{GA}:SA\rightarrow S^2A$$
  Thus, we have natural transformation $\s{}$ and morphism $\s{I}$ defined as:
  $$\s{A,B}=F\n{A,B}\circ\m{GA,GB}:SA\tri SB\rightarrow SA\tri SB \qquad\qquad\qquad
  \s{I}=F\n{I'}\circ\m{I}:I'\rightarrow SI'$$
  The comonad $S$ being monoidal means
  \begin{enumerate}
  \item $S$ is a monoidal functor, i.e. the following diagrams commute:
        \begin{mathpar}
        \bfig
          \hSquares/->`->`->``->`->`->/<400>[
            (SA\tri SB)\tri SC`SA\tri(SB\tri SC)`SA\tri S(B\tri C)`
            S(A\tri B)\tri SC`S((A\tri B)\tri C)`S(A\tri(B\tri C));
            \alpha_{SA,SB,SC}'`id_{SA}\tri\s{B,C}`\s{A,B}\tri id_{SC}``
            \s{A,B\tri C}`\s{A\tri B,C}`S\alpha_{A,B,C}']
        \efig
        \and
        \bfig
          \square/->`->`<-`->/<600,400>[
            I'\tri SA`SA`SI'\tri SA`S(I'\tri A);
            \lambda_{SA}'`\s{I'}\tri id_{SA}`S\lambda_A'`\s{I',A}]
        \efig
        \and
        \bfig
          \square/->`->`<-`->/<600,400>[
            SA\tri I'`SA`SA\tri SI'`S(A\tri I');
            \rho_{SA}'`id_{SA}'\tri\s{I'}`S\rho_A'`\s{A,I'}]
        \efig
        \end{mathpar}
  \item $\varepsilon$ is a monoidal natural transformation:
        \begin{mathpar}
        \bfig
          \square/->`->`->`=/<600,400>[
            SA\tri SB`S(A\tri B)`A\tri B`A\tri B;
            \s{A,B}`\varepsilon_A\tri\varepsilon_B`\varepsilon_{A\tri B}`]
        \efig
        \and
        \bfig
          \Vtriangle/->`<-`=/<400,400>[SI'`I'`I';\varepsilon_{I'}`\s{I'}`]
        \efig
        \end{mathpar}
  \item $\delta$ is a monoidal natural transformation:
        \begin{mathpar}
        \bfig
          \square/->`->`->`/<1500,400>[
            SA\tri SA`S(A\tri B)`S^2A\tri S^2B`S^2(A\tri B);
            \s{A,B}`\delta_A\tri\delta_B`\delta_{A\tri B}`]
          \morphism<800,0>[S^2A\tri S^2B`S(SA\tri SB);\s{SA,SB}]
          \morphism(800,0)<700,0>[S(SA\tri SB)`S^2(A\tri B);S\s{A,B}]
        \efig
        \and
        \bfig
          \square/->`<-`<-`->/<400,400>[
            SI'`S^2I'`I'`SI';\delta_{I'}`\s{I'}`S\s{I'}`\s{I'}]
        \efig
        \end{mathpar}
  \end{enumerate}
  The proof for the commutativity of the diagrams are similar as the proof in
  Lemma~\ref{lem:monoidal-monad}. We do not include the proof here for simplicity.
\end{proof}

We then show that the co-Eilenberg-Moore category of the comonad $S$ is symmetric monoidal
closed.

@@

\begin{lemma}
  \label{lem:em-exchange}
  Given a LAM $(\cat{C},\cat{L},F,G,\eta,\varepsilon)$ and the comonad $S$ on $\cat{L}$,
  the co-Eilenberg-Moore category $\cat{L}^S$ has an exchange natural transformation
  $\e{A,B}^S:A\tri B\rightarrow B\tri A$.
\end{lemma}
\begin{proof}
  We define the exchange $\e{A,B}^S:A\tri B\rightarrow B\tri A$ as
  $$\bfig
    \morphism<600,0>[A\tri B`FGA\tri FGB;h_A\tri h_B]
    \morphism(600,0)<800,0>[FGA\tri FGB`F(GA\otimes GB);\m{GA,GB}]
    \morphism(1400,0)<800,0>[F(GA\otimes GB)`F(GB\otimes GA);F\e{GA,GB}]
    \morphism(2200,0)<700,0>[F(GB\otimes GA)`FG(B\tri A);F\n{B,A}]
    \morphism(2900,0)<500,0>[FG(B\tri A)`B\tri A;\varepsilon_{B\tri A}]
  \efig$$
  in which $(F,\m{})$ and $(G,\n{})$ are monoidal functors, and $\e{}$ is the exchange for
  $\cat{C}$. Then $\e{}^S$ is a natural transformation because the following diagrams commute
  for morphisms $f:A\rightarrow A'$ and $g:B\rightarrow B'$:
  \begin{mathpar}
  \bfig
    \square|almb|<700,400>[
      A\tri B`FGA\tri FGB`A'\tri B'`FGA'\tri FGB';
      h_A\tri h_B`f\tri g`FGf\tri FGg`h_{A'}\tri h_{B'}]
    \square(700,0)|ammb|/->``->`->/<800,400>[
      FGA\tri FGB`F(GA\otimes GB)`FGA'\tri FGB'`F(GA'\otimes GB');
      \m{GA,GB}``F(Gf\otimes Gg)`\m{GA',GB'}]
    \square(1500,0)|ammb|/->``->`->/<800,400>[
      F(GA\otimes GB)`F(GB\otimes GA)`F(GA'\otimes GB')`F(GB'\otimes GA');
      F\e{A,B}``F(Gg\otimes Gf)`F\e{A',B'}]
    \square(2300,0)|ammb|/->``->`->/<800,400>[
      F(GB\otimes GA)`FG(B\tri A)`F(GB'\otimes GA')`FG(B'\tri A');
      F\n{B,A}``FG(g\tri f)`F\n{B',A'}]
    \square(3100,0)|amrb|/->``->`->/<600,400>[
      FG(B\tri A)`B\tri A`FG(B'\tri A')`B'\tri A';
      \varepsilon_{B\tri A}``g\tri f`\varepsilon_{B'\tri A'}]
  \efig
  \end{mathpar}
\end{proof}

@@

    \Vtrianglepair|aammm|/->`->`<-``<-/<1100,400>[

@@

    \qtriangle(2200,0)|amr|/=`<-`->/<1000,400>[

@@

    \dtriangle(1100,0)|mmm|/`<-`->/<1100,400>[

@@

    \btriangle(0,-400)|lmm|/->`<-`/<1100,400>[

@@

    \btriangle(1100,-400)|mmm|/<-``->/<2100,400>[

@@

    \qtriangle(2200,-400)|mmr|/`<-`->/<1000,400>[

@@

    \btriangle(0,-800)|lmm|/->`<-`/<2200,400>[

@@

    \morphism(1100,-400)|m|<1100,-400>[

@@

    \dtriangle(2200,-800)|mra|/`->`->/<1000,400>[

@@

    \square(0,-1300)|almb|/<-`->`->`->/<1100,500>[

@@

    \morphism(1100,-800)|b|/<-/<1100,0>[

@@

    \dtriangle(1100,-1300)/`->`<-/<2100,500>[

@@

    \morphism(1100,-800)|m|<2100,-500>[

@@

    \morphism(550,50)//<0,0>[`;(1)]
    \morphism(550,-300)//<0,0>[`;(2)]

@@

    \morphism(550,-1000)//<0,0>[`;(4)]
    \morphism(1100,300)//<0,0>[`;(5)]
    \morphism(1900,200)//<0,0>[`;(6)]

@@

    \morphism(1550,-1050)//<0,0>[`;(9)]
    \morphism(2700,-950)//<0,0>[`;(10)]
    \morphism(3000,300)//<0,0>[`;(11)]
    \morphism(2700,50)//<0,0>[`;(12)]

@@

  The third diagram commutes as follows: (1) and (7)--Lemma~\ref{lem:em-ex}; (2)--naturality of
  $\alpha'$; (3) and (8)--naturality of $\varepsilon$; (4), (6) and (12)--G is a monoidal
  functor; (5)--$\cat{C}$ is symmetrical monoidal closed; (9)--coalgebra; (10)--$\varepsilon$
  is a monoidal natural transformation; (11)--naturality of $\e{}$.

@@

    \morphism(2200,-2000)|m|<0,-600>[

@@

    \morphism(1500,-2200)|m|<-500,-400>[
      F(GB\otimes G(A\tri C))`FG(B\tri(A\tri C));F\n{B,A\tri C}]

@@

    \morphism(1000,-2600)|m|<-1000,0>[

@@

    \morphism(3200,-3000)|m|<-1000,400>[FG((B\tri C)\tri A)`FG(B\tri(C\tri A));FG\alpha_{B,C,A}]

@@

    \morphism(2200,-2600)|m|<-2200,-400>[
      FG(B\tri(C\tri A))`B\tri(C\tri A);\varepsilon_{B\tri(C\tri A)}]
    \morphism(800,-2000)|m|<200,-600>[FG((B\tri A)\tri C)`FG(B\tri(A\tri C));FG\alpha'_{B,A,C}]
    \morphism(300,-700)//<0,0>[`;(1)]
    \morphism(500,-2200)//<0,0>[`;(2)]
    \morphism(1500,100)//<0,0>[`;(3)]
    \morphism(1500,-500)//<0,0>[`;(4)]
    \morphism(1500,-1100)//<0,0>[`;(5)]
    \morphism(1100,-2200)//<0,0>[`;(6)]
    \morphism(1800,-2400)//<0,0>[`;(7)]
    \morphism(2000,-2800)//<0,0>[`;(8)]
    \morphism(2450,200)//<0,0>[`;(9)]
    \morphism(2900,-300)//<0,0>[`;(10)]
    \morphism(2800,-1200)//<0,0>[`;(11)]
    \morphism(2720,-2200)//<0,0>[`;(12)]
